Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-08-23 README.Rmd
further pruning and add renv support
repository clean up

# Evaluating Semi-Parametric Nowcasts of COVID-19 Hospital Admissions in Germany

This repository contains the documentation, results, and code of a project evaluating ... See the documentation for further details.

@@

## Documentation

```{r, child = "docs/chunks/documentation.Rmd", eval = TRUE}
```

## Key files and folders

Folder/File | Purpose
---|---
[`writeup`](docs/) | Summary paper and additional supplementary information as `Rmarkdown` documents.
[`_targets.Rmd`](_targets.Rmd) | Analysis workflow for interactive use.
[`R`](R/) | R functions used in the analysis and for evaluation.
[`data`](data/) | Input data and summarised output generated by steps in the analysis.
[`.devcontainer`](.devcontainer/) | Resources for reproducibility using `vscode` and `docker`.

@@

## Analyses

>>>>

# Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

This repository contains the documentation, results, and code of a project evaluating a simplified forecasting model in comparison the ECDC forecasting hub ensemble. See the documentation for further details.

@@

## Project structure

Folder | Purpose
---|---

[`ecdc-weekly-growth-forecasts`](ecdc-weekly-growth-forecasts/) | The code for the simplified forecasting model evaluated in this work.
[`data-raw`](data-raw/) | Raw input data and scripts required to download and process it.
[`data`](data/) | Processed data from `data-raw` ready to be used in the paper analysis.
[`R`](R/) | R functions used in the analysis and for evaluation.
[`paper`](paper/) | Summary paper and additional supplementary information as `Rmarkdown` documents.
[`.devcontainer`](.devcontainer/) | Resources for reproducibility using `vscode` and `docker`.

@@

### 2022-08-23 paper/paper.Rmd
repository clean up

---
title: Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble
preprint: false
author: 
  - name: Sam Abbott
    affiliation: 1
    corresponding: true
    email: sam.abbott@lshtm.ac.uk
  - name:  Johannes Bracher
    affiliation: 2
  - name: Sebastian Funk
    affiliation: 1
affiliation:
  - code: 1
    address: London School of Hygiene and Tropical Medicine, London, UK
  - code: 2
    address: Chair of Statistics and Econometrics, Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany
abstract: > 
  We made the best model. It is both simple and amazing.
bibliography: library.bib
output:
  bookdown::pdf_book:
    base_format: rticles::peerj_article
    extra_dependencies: ["float"]
---

@@

There was also substantial variation across forecast locations with the surrogate performing well in some locations at some forecast horizons, for example the four week horizon in the United Kingdom, and badly in others, for example the four week forecast in Switzerland (Figure \@ref(fig: assemble-eval) c).
In general, across locations, as observed overall, relative forecast performance was comparable across horizons though with a heavier right tail at longer horizons. Some locations showed less of this behaviour, for example Spain, and in some it was very dominant, for exampel Switzerland.

@@

Overall the surrogate model was well calibrated at the 30%, 60% and 90% credible intervals whilst the ensemble model was in general poorly calibrated with calibration becoming worse at larger credible intervals (at 30%, at 60%, and at 90%).
When stratified by forecast horizon the ensemble forecast was best calibrated at the one week forecast horizon and then became progressively less well calibrated as foreast horizon increased with the worst calibration at the 90% credible interval (Figure \@ref(fig:plot-coverage) a). 
In comparison the surrogate forecast was less well calibrated at the one week forecast horizon with a tendancy to have a larger empirical coverage than required at longer horizons the surrogate forecast transioned to being well calibrated and then had a lower coverage than optimal though to a much lower degree than the ensemble forecast.
This was not the case for the 90% credible interval where the surrogate model stably covered slightly more than the expected interval indicating forecasts were somewhat overly uncertain for this intervals.

>>>>

---
title: Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble
preprint: true
author: 
  - name: Sam Abbott
    affiliation: 1
    corresponding: true
    email: sam.abbott@lshtm.ac.uk
  - name:  Johannes Bracher
    affiliation: 2
  - name: Sebastian Funk
    affiliation: 1
affiliation:
  - code: 1
    address: London School of Hygiene and Tropical Medicine, London, UK
  - code: 2
    address: Chair of Statistics and Econometrics, Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany
abstract: > 
  We made the best model. It is both simple and amazing.
bibliography: library.bib
output:
  bookdown::pdf_book:
    base_format: rticles::peerj_article
    extra_dependencies: ["float"]
---

@@

There was also substantial variation across forecast locations with the surrogate performing well in some locations at some forecast horizons, for example the four week horizon in the United Kingdom, and badly in others, for example the four week forecast in Switzerland (Figure \@ref(fig:assemble-eval) c).
In general, across locations, as observed overall, relative forecast performance was comparable across horizons though with a heavier right tail at longer horizons. Some locations showed less of this behaviour, for example Spain, and in some it was very dominant, for example Switzerland.

@@

Overall the surrogate model was well calibrated at the 30%, 60% and 90% credible intervals whilst the ensemble model was in general poorly calibrated with calibration becoming worse at larger credible intervals.
When stratified by forecast horizon the ensemble forecast was best calibrated at the one week forecast horizon and then became progressively less well calibrated as foreast horizon increased with the worst calibration at the 90% credible interval (Figure \@ref(fig:plot-coverage) a). 
In comparison the surrogate forecast was less well calibrated at the one week forecast horizon with a tendancy to have a larger empirical coverage than required at longer horizons the surrogate forecast transioned to being well calibrated and then had a lower coverage than optimal though to a much lower degree than the ensemble forecast.
This was not the case for the 90% credible interval where the surrogate model stably covered slightly more than the expected interval indicating forecasts were somewhat overly uncertain for this intervals.
